%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{awesome-cv}
% \usepackage{fontspec} % Removed as awesome-cv.cls handles it.

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm}
\fontdir[fonts/]
\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% --- Personal Information ---
\name{Brian J}{Glusman}
\address{651 Vanderbilt St, Apt 3X, Brooklyn, NY}
\mobile{215-460-9585} % Reinstated with plain text, no icon call yet
\email{brian@glusman.me} % Reinstated with plain text, no icon call yet
% \homepage{}
% \github{}
% \linkedin{}
\position{Engineering Manager{\enskip|\enskip}Elixir Developer}
\quote{``Experienced engineering manager and developer with expertise in Elixir, Phoenix, \\ and data analytics platforms. Strong background in technical leadership, system architecture, \\ and mentoring engineers.''} 
\makecvfooter{\today}{Brian J Glusman~~~|~~~R\'esum\'e}{\thepage}

\begin{document}
\makecvheader

% --- Education --- 
\cvsection{Education}
\begin{cventries}
  \cventry
    {B.A. in Computer Science}
    {Bowdoin College}
    {Brunswick, Maine}
    {May 2001}
    {
      \begin{cvitems}
        \item GPA in Major: 3.8
        \item SAT: 1570 (800 Math, 770 Verbal)
      \end{cvitems}
    }
  \cventry
    {N/A}
    {Recurse Center}
    {New York City, NY}
    {Spring 2015}
    {
      \begin{cvitems}
        \item Self-directed programmer retreat focused on open source and deep technical skill-building.
      \end{cvitems}
    }
\end{cventries}

% --- Skills --- 
\cvsection{Skills}
\begin{cvskills}
  \cvskill{Programming Languages}{Elixir, Ruby, JavaScript, Objective-C, SQL}
  \cvskill{Frameworks \& Libraries}{Phoenix, Rails, Backbone, GraphQL}
  \cvskill{Tools \& Platforms}{Kubernetes, Snowflake, Docker, Git, Linux (Ubuntu, RedHat, CentOS)}
  \cvskill{Open Source Contributions}{\parbox[t]{0.7\linewidth}{live\_dashboard\_history, phx\_live\_dashboard PR,\\ avalanche, ayesql}} 
\end{cvskills}

% --- Experience --- 
\cvsection{Experience}
\begin{cventries}
  \cventry
    {Engineering Manager – Executive Intelligence Reporting \& Analytics Platform}
    {PepsiCo}
    {New York City, NY}
    {July 2020 – Present}
    {
      \begin{cvitems}
        \item Started as Senior Backend Engineer in supply chain (Elixir, Phoenix, GraphQL).
        \item Promoted to Engineering Lead (2021) managing warehouse order processing.
        \item Promoted to Engineering Manager (late 2021), supervising junior and mid-level engineers.
        \item Shifted focus mid-2022 to overall order processing, and in 2024 to executive intelligence reporting.
        \item Led automation tooling, improved Snowflake query processes, developed widely-used internal frameworks,
        \item and mentored multiple engineers.
      \end{cvitems}
    }
  \cventry
    {Director of Technology / Tech Lead}
    {Stella Service, Inc. / PowerReviews, Inc.}
    {New York City, NY / Chicago, IL (remote)}
    {August 2015 – February 2019}
    {
      \begin{cvitems}
        \item Led transformation of prototype to enterprise feature set, introduced hierarchical modeling, SAML authentication,
        \item microservice API with high uptime.
        \item Pioneered Kubernetes and Elixir/Phoenix adoption.
        \item Managed product through acquisition and legacy platform migration.
      \end{cvitems}
    }
\end{cventries}

% --- Projects --- 
\cvsection{Projects}
\begin{cventries}
  \cventry
    {live\_dashboard\_history}
    {https://github.com/bglusman/live\_dashboard\_history}
    {Phoenix LiveDashboard Plugin}
    {Ongoing}
    {
      \begin{cvitems}
        \item Plugin for Phoenix LiveDashboard that adds historical metrics tracking.
        \item Technologies: Elixir, Phoenix, Telemetry
      \end{cvitems}
    }
\end{cventries}

\end{document}
